Simulating Financial Markets using MASON Framework\thanks{Prepared for the 2nd World Congress on Social Simulation, GMU, Fairfax, 14--17 July, 2008.}

### 2008-05-08 documents/WCSS2008Paper/paper.tex

TODO Note: liquidity issues

@@

TODO: show results side by side with original papers' figures

These compare well with data shown in the original paper (shown in Figures \ref{fig:ContSmallSPap} and \ref{fig:ContLargeSPap}).

@@

    \caption{Autocorrelation and distributions in Cont simulation with $s=0.1$ and varying $D$, averaged over many runs. In bottom row, kernel regresion on Hurst exponents of time series generated from Con't model for varying levels of $s$ and $D$ is presented.}
    \label{fig:ContMultiRun}
  \end{center}
\end{figure}

>>>>

@@

The supreme objective was to recreate results reported by others rather than to create a standalone model of the market. Therefore, the validation focused on comparing outputs from our simulations to graphs and statistics from other papers. These compare well with data shown in the original paper (shown in Figures \ref{fig:ContSmallSPap} and \ref{fig:ContLargeSPap}).

@@

    \caption{Autocorrelation and distributions in Cont simulation with $s=0.1$ and varying $D$, averaged over many runs. In bottom row, kernel regresion with 95\% resampled confidence intervals on Hurst exponents of time series generated from Con't model for varying levels of $s$ and $D$ is presented.}
    \label{fig:ContMultiRun}
  \end{center}
\end{figure}
